\section{Concepts in Particle Physics}
\paragraph{a)} The experimental evidence of quarks comes mainly from high energy particle collisions. In particular deep inelastic scattering, where by shooting electrons at high speeds on protons and neutrons and measuring how the electron scatters. If the proton and neutrons where elementary particles and did not contain quarks, we would expect a relatively elastic scattering on the `surface of the atom'. Instead one measured inelastic scattering and angles which showed scattering inside of the hadron, that is, the electron scattering on the quarks on the inside.

\paragraph{b)} The main experimental evidence is the production of three jets in particle collisions. Especially the electron positron annihilation at DESY in Hamburg 1979. When colliding the particles in high energy they release jets of hadrons. Since quarks come only in pairs one would expect to always see an even number of jets. However, if there is an odd number of jets it suggests that there is another particle as well, this is what was found.

\paragraph{c)} They are related due to flavor mixing which couples the flavor eigenstates $(d^f, s^f, b^f)$ and $(\nu_e, \nu_\mu, \nu_\tau)$ to the mass eigenstates $(d, s, b)$ and $(\nu_1, \nu_2, \nu_3)$, respectively. They can be described as a rotation with the help of a rotation matrix, the CKM-matrix for quarks and the PMNS-matrix for neutrinos. What this essentially means is that the flavor eigenstates is described as a superposition of the mass eigenstates.

\paragraph{d)} From the electroweak theory the $W^\pm$ and $Z^0$ bosons as well as the photon should all be massless. However, experiments showed that only the photons was massless and the other particles had mass. The Higgs mechanism solves this by giving mass to the the $W^\pm$ and $Z^0$ bosons, as well as quarks and leptons, but not neutrinos, their mass is not explained by the standard model. The quantum particle associated with the Higgs field and Higgs mechanism, is the Higgs boson. Similar to how the electromagnetic field has photons as a quantum particle, the Higgs field has the Higgs boson.